---
title: "About"
description:
site: distill::distill_website
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I’m Alex Oliver, chief data scientist at ES Partners / Evolving Strategies in Washington, D.C. I use the scientific method to change people’s opinions and behavior at scale for clients. I conduct survey and field experiments, use Bayesian statistics and machine learning, and primarily code in R.

I help Fortune 500 companies and political independent expenditure organizations. Since 2017, I’ve led over 50 research engagements that have impacted over 100 million consumers and voters.

<aside>
Here's an aside.
```{r}
library(tidyverse)
ggplot(mtcars, aes(hp, mpg)) + geom_point() + geom_smooth()
```
</aside>

My research has been presented to Capitol Hill and the White House. It has also been covered in *The New Yorker*, *Politico*, *Adweek*, and other media.

$$
\sigma = \sqrt{ \frac{1}{N} \sum_{i=1}^N (x_i -\mu)^2}
$$

I’ve held lectureships at Brandeis University and Boston University. I’ve also taught courses on public opinion, voter behavior, and campaign strategy.

I have a Ph.D. in political science from Boston University. I also have an M.A. in economics from Tufts University and a B.A. in economics from Merrimack College.

## Acknowledgements{.appendix}

This is pretty awesome. Compared to Hugo, that is.


